Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-10-21 paper/paperv3.qmd
Updated effect size tables

#Making the tables
#Not sure about this function
  # effect_size <- function(m) {
  #   probs <- tibble(age = c(15, 19),
  #                   age_cat = c("Old", "Old")) %>% 
  #     mutate(age10 = (age - a) / 10) %>% 
  #     predict(m, re.form = NA, newdata = ., type = "response")
  #   odds <- probs / (1 - probs)
  #   odds[2] / odds[1]
  # }

  list(
    h1 = summary(breed_age_mod)$coefficients,
    h2_surv = summary(pup_surv_mod)$coefficients,
    h2_recr = summary(pup_recr_mod)$coefficients,
    h3 = summary(sexrat_age_mod)$coefficients,
    h4_molt = summary(molt_mod)$coefficients, 
    h4_breed = summary(breed_mod)$coefficients,
    h1_aic = AIC(breed_age_mod),
    h2_surv_aic = AIC(pup_surv_mod),
    h2_recr_aic = AIC(pup_recr_mod),
    h3_aic = AIC(sexrat_age_mod),
    h4_molt_aic = AIC(molt_mod), 
    h4_breed_aic = AIC(breed_mod)
    # h1_effect = effect_size(breed_age_mod),
    # h2_surv_effect = effect_size(pup_surv_mod),
    # h2_recr_effect = effect_size(pup_recr_mod),
    # h3_effect = effect_size(sexrat_age_mod)
  )
}

@@

```{r}
# Are hypotheses supported by the model? note to future readers...this part could have been done way easier, and you will have to trust our process that this was the path of least resistence for us at the point of final revisions!
# extract_p <- function(h, tails = 1) {
#   if (tails == 1) {
#     map_dbl(mod_sens, \(m) pnorm(m[[h]]["age10:age_catOld", "z value"]))
#   } else if (tails == 2) {
#     map_dbl(mod_sens, \(m) 2 * pnorm(m[[h]]["age10:age_catOld", "z value"],
#                                      lower.tail = (m[[h]]["age10:age_catOld", "z value"] < 0)
#                                      ))
#   } else {
#     stop("tails must be 1 or 2")
#   }
# }
extract_p <- function(h) {
  map_dbl(mod_sens, \(m) m[[h]]["age10:age_catOld", "Pr(>|z|)"])
}
extract_aic <- function(h) {
  map_dbl(mod_sens, paste(h, "aic", sep = "_"))
}
aic_weight <- function(x) {
  rellik <- exp(-0.5 * (x - min(x)))
  rellik / sum(rellik)
}
extract_coef <- function(h) {
  map_dbl(mod_sens, \(m) m[[h]]["age10:age_catOld", "Estimate"])
}
extract_se <- function(h) {
  map_dbl(mod_sens, \(m) m[[h]]["age10:age_catOld", "Std. Error"])
}

@@

knitr::kable(p_tbl)
knitr::kable(aic_tbl)
knitr::kable(coef_tbl)

@@

left_join(
  pivot_longer(p_tbl, -age_cutoff, names_to = "hypothesis", values_to = "p"),
  pivot_longer(coef_tbl, -age_cutoff, names_to = "hypothesis", values_to = "coef"),
  by = c("age_cutoff", "hypothesis")
  ) %>% 
  left_join(
    pivot_longer(se_tbl, -age_cutoff, names_to = "hypothesis", values_to = "se"),
    by = c("age_cutoff", "hypothesis")
  ) %>% 
  ggplot(aes(age_cutoff, coef)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_pointrange(aes(size = p, 
                      color = p < 0.05, 
                      ymin = coef - 1.96 * se,
                      ymax = coef + 1.96 * se)) +
  labs(x = "Senescence onset (years)") +
  scale_size_continuous(range = c(0.25, 1)) +
  expand_limits(y = 3) +
  facet_wrap(~hypothesis) +
  theme(legend.position = "none")

@@

  geom_line(aes(age, predicted, group = interaction(phase, age_cat, year_fct)), 
            filter(phen_pred_years, phase == "breeddur"),
            alpha = 0.1) +

>>>>

  list(
    h1 = summary(breed_age_mod)$coefficients,
    h2_surv = summary(pup_surv_mod)$coefficients,
    h2_recr = summary(pup_recr_mod)$coefficients,
    h3 = summary(sexrat_age_mod)$coefficients,
    h4_molt = summary(molt_mod)$coefficients, 
    h4_breed = summary(breed_mod)$coefficients,
    h1_aic = AIC(breed_age_mod),
    h2_surv_aic = AIC(pup_surv_mod),
    h2_recr_aic = AIC(pup_recr_mod),
    h3_aic = AIC(sexrat_age_mod),
    h4_molt_aic = AIC(molt_mod), 
    h4_breed_aic = AIC(breed_mod)
  )
}

@@

```{r}
# Are hypotheses supported by the model? note to future readers...this part could have been done way easier, and you will have to trust our process that this was the path of least resistence for us at the point of final revisions!
# extract_p <- function(h, tails = 1) {
#   if (tails == 1) {
#     map_dbl(mod_sens, \(m) pnorm(m[[h]]["age10:age_catOld", "z value"]))
#   } else if (tails == 2) {
#     map_dbl(mod_sens, \(m) 2 * pnorm(m[[h]]["age10:age_catOld", "z value"],
#                                      lower.tail = (m[[h]]["age10:age_catOld", "z value"] < 0)
#                                      ))
#   } else {
#     stop("tails must be 1 or 2")
#   }
# }
extract_p <- function(h) {
  map_dbl(mod_sens, \(m) m[[h]]["age10:age_catOld", "Pr(>|z|)"])
}
extract_aic <- function(h) {
  map_dbl(mod_sens, paste(h, "aic", sep = "_"))
}
aic_weight <- function(x) {
  rellik <- exp(-0.5 * (x - min(x)))
  rellik / sum(rellik)
}
extract_coef <- function(h) {
  #map_dbl(mod_sens, \(m) m[[h]]["age10:age_catOld", "Estimate"])
  exp(map_dbl(mod_sens, \(m) m[[h]]["age10:age_catOld", "Estimate"]))
}
extract_se <- function(h) {
  map_dbl(mod_sens, \(m) m[[h]]["age10:age_catOld", "Std. Error"])
}

@@

knitr::kable(p_tbl, 
             caption = "P values for threshold ages 6-14")
knitr::kable(aic_tbl, 
             caption = "AIC weights for threshold ages 6-14")
knitr::kable(coef_tbl, 
             caption = "Effect size for threshold ages 6-14")

@@

left_join(
  pivot_longer(p_tbl, -age_cutoff, names_to = "hypothesis", values_to = "p"),
  pivot_longer(coef_tbl, -age_cutoff, names_to = "hypothesis", values_to = "coef"),
  by = c("age_cutoff", "hypothesis")
  ) %>% 
  left_join(
    pivot_longer(se_tbl, -age_cutoff, names_to = "hypothesis", values_to = "se"),
    by = c("age_cutoff", "hypothesis")
  ) %>% 
  ggplot(aes(age_cutoff, coef)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_pointrange(aes(size = p, 
                      color = p < 0.05, 
                      ymin = coef - 1.96 * se,
                      ymax = coef + 1.96 * se)) +
  labs(x = "Senescence onset (years)", 
       y = "Effect size") +
  scale_size_continuous(range = c(0.25, 1)) +
  expand_limits(y = 3) +
  facet_wrap(~hypothesis) +
  theme(legend.position = "none")

@@
